demographicvariablesregression

### 2023-09-20 combined data set/DVgraphs.Rmd
wilcoxon rank sum test on caste and urban_rural
lot of changes because I wasn't opening the project file.

@@

library(emmeans)
emm_results <- emmeans(kruskal_results, ~ technology)
summary(emm_results, infer = c(T, T))

@@

```{r}
#now do the same for perceived benefit
#null hypothesis - no sognificant difference between perceived benefit from technologies. 
#push to github - figure out what happened! why not pushing anymore yaar 
#

@@

```
```{r}
library(dplyr)
perceivedbenefit %>%
  group_by(technology) %>%
  summarise(
    count = n(),
    mean = mean(perceived_benefit, na.rm = TRUE),
    sd = sd(perceived_benefit, na.rm = TRUE),
    median = median(perceived_benefit, na.rm = TRUE),
    IQR = IQR(perceived_benefit, na.rm = TRUE)
  )

@@

>>>>

ggplot(perceivedrisk, aes(x = perceived_risk, y = technology)) + 
  geom_violin()
#the violin graph shows that the data is definitely not normally distributed

@@

#library(emmeans)
#emm_results <- emmeans(kruskal_result, ~ technology)
#summary(emm_results, infer = c(T, T))

@@

@@

```{r}
library(dplyr)
perceivedbenefit %>%
  group_by(technology) %>%
  summarise(
    count = n(),
    mean = mean(perceived_benefit, na.rm = TRUE),
    sd = sd(perceived_benefit, na.rm = TRUE),
    median = median(perceived_benefit, na.rm = TRUE),
    IQR = IQR(perceived_benefit, na.rm = TRUE)
  )

@@

```{r, echo=FALSE}
# Calculate median and IQR for each technology and category (risk or benefit)
summary_df_median <- long_format %>%
  group_by(technology, risk_or_benefit) %>%
  summarise(median = median(value, na.rm = TRUE),
            IQR = IQR(value, na.rm = TRUE),
            .groups = "drop")

# Order technologies by median risk
order_risk_median <- summary_df_median %>% 
  filter(risk_or_benefit == "risk") %>%
  arrange(median) %>% 
  pull(technology)

# Change the levels of factor 'technology'
summary_df_median$technology <- factor(summary_df_median$technology, levels = order_risk_median)

# Plotting the data
ggplot(summary_df_median, aes(x = technology, y = median, fill = risk_or_benefit)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = median - 0.5*IQR, ymax = median + 0.5*IQR), 
                width = 0.3, position = position_dodge(0.9)) +
  ylim(0, 5) +
  scale_fill_manual("legend", 
                    values = c("benefit" = "palegreen3", "risk" = "firebrick2"), 
                    labels = c("benefit" = "Perceived Benefit", "risk" = "Perceived Risk")) +
  labs(y = "Median Values", x = "Energy Technologies", fill = "Perceived") +
  ggtitle("Perceived risk and benefit from centrally owned energy technologies\n(Median)") +
  coord_flip()

# **Perceived risk by Support for Totalitarian government**

#The following is a list of statements about governance. How strongly do you agree or disagree with each of these statements? Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)? - It is good to have a strong leader who does not have to bother with elections.

govtrisk$grouped_total <- ifelse(govtrisk$SYSTEMTOTAL %in% c(1,2), "low", ifelse(govtrisk$SYSTEMTOTAL %in% c(4,5), "high", NA))

totalrisk2 <- govtrisk %>%
  group_by(grouped_total) %>%
  filter(grouped_total %in% c("low", "high")) %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
  dplyr::select(grouped_total, technology, summary) %>%
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  separate(var, c("technology", "meansd")) %>%
  spread(meansd,summary) %>%
  select(-Risky) %>%
  arrange(grouped_total)

data.frame(totalrisk2)

totalrisk2 <- totalrisk2 %>%
  mutate(technology = reorder(technology, -mean))  # reorder based on -mean, to get high to low

t <- totalrisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = grouped_total))+
  geom_line(aes(colour = grouped_total, line = grouped_total)) +
  labs(y = "mean perceived risk", x = "energy technology", color = "Totalitarianism Value") +
  ggtitle("Q:It is good to have a strong leader who does not have to bother with\nelections.")

t

# **Perceived risk by Support for Technocratic government**

#The following is a list of statements about governance. How strongly do you agree or disagree with each of these statements? Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)? - Experts, not the government, should make decisions according to what they think is best for the country.

govtrisk$grouped_techno <- ifelse(govtrisk$SYSTEMTECHNO %in% c(1,2), "low", ifelse(govtrisk$SYSTEMTECHNO %in% c(4,5), "high", NA))

technorisk2 <- govtrisk %>%
  group_by(grouped_techno) %>%
  filter(grouped_techno %in% c("low", "high")) %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
  dplyr::select(grouped_techno, technology, summary) %>%
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  separate(var, c("technology", "meansd")) %>%
  spread(meansd,summary) %>%
  select(-Risky) %>%
  arrange(grouped_techno)

data.frame(technorisk2)

technorisk2 <- technorisk2 %>%
  mutate(technology = reorder(technology, -mean))  # reorder based on -mean, to get high to low

techno <- technorisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = grouped_techno))+
  geom_line(aes(colour = grouped_techno, line = grouped_techno)) +
  labs(y = "mean perceived risk", x = "energy technology", color = "Technocratic Value") +
  ggtitle("Q:Experts, not the government, should make decisions according to\nwhat they think is best for the country.")

techno

# **Perceived risk by Support for Religious government**

#The following is a list of statements about governance. How strongly do you agree or disagree with each of these statements? Do you strongly disagree(1), somewhat disagree(2), neither agree nor disagree(3), somewhat agree(4) or strongly agree(5)? - There should be a system governed by religious law.

govtrisk$grouped_religion <- ifelse(govtrisk$SYSTEMRELIGION %in% c(1,2), "low", ifelse(govtrisk$SYSTEMRELIGION %in% c(4,5), "high", NA))

religionrisk2 <- govtrisk %>%
  group_by(grouped_religion) %>%
  filter(grouped_religion %in% c("low", "high")) %>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd, Risky_Hydro_n, Risky_Solar_n, Risky_Wind_n, Risky_Nuclear_n, Risky_Coal_n, Risky_Gas_n, Risky_Oil_n) %>%
  dplyr::select(grouped_religion, technology, summary) %>%
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  separate(var, c("technology", "meansd")) %>%
  spread(meansd,summary) %>%
  select(-Risky) %>%
  arrange(grouped_religion)

data.frame(religionrisk2)

religionrisk2 <- religionrisk2 %>%
  mutate(technology = reorder(technology, -mean))  # reorder based on -mean, to get high to low

r <- religionrisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = grouped_religion))+
  geom_line(aes(colour = grouped_religion, line = grouped_religion)) +
  labs(y = "mean perceived risk", x = "energy technology", color = "Religious law Value") +
  ggtitle("Q:There should be a system governed by religious law.")

r
```

### 2023-09-20 combined data set/demovariablesregression.Rmd
lot of changes because I wasn't opening the project file.

```{r, eval =TRUE, echo=FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

@@

```{r}
library(dplyr)

demovars <- joineddf %>%
  select(starts_with("Risky"), starts_with("Ben"),urban_rural, gender, caste, religion, age, State)%>%
  mutate(religion = ifelse(religion == "Other (Please mention)", "Other", religion))

@@

```{r}
library(dplyr)

@@

@@

@@

demovars_mf <- demovars %>% 
  filter(gender %in% c("Male", "Female"))

wilcox_gender <- demovars_mf %>%
  select(starts_with("Risky")) %>%
  lapply(function(col) wilcox.test(col ~ gender, data = demovars_mf))

@@

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

demovars_caste_long <- demovars_caste %>%
  pivot_longer(cols = starts_with("Risky_"), names_to = "technology", values_to = "perceived_risk") %>%
  mutate(technology = gsub("Risky_", "", technology)) %>%
        mutate(caste = ifelse(grepl("SC|Scheduled caste", caste), "SC", caste),
              caste = ifelse(grepl("ST|Scheduled Tribe", caste), "ST", caste),
              caste = ifelse(grepl("OBC|Other Backward Classes", caste), "OBC", caste))

@@

@@

>>>>

```{r, eval =TRUE, echo=FALSE}
#This chunk contains the coding schemes of likert scales 
codedmodule1 <- module1 %>%

@@

```{r, echo=FALSE}

# cleaning up variables and making them into neat categories, turning IVs into factors

library(dplyr)

demovars <- joineddf %>%
  dplyr::select(starts_with("Risky"), starts_with("Ben"),urban_rural, gender, caste, religion, age, State)%>%
  mutate(religion = ifelse(religion == "Other (Please mention)", "Other", religion)) %>%
  filter(gender %in% c("Male", "Female"))%>%
  mutate(caste = ifelse(grepl("SC|Scheduled caste", caste), "SC", caste),
          caste = ifelse(grepl("ST|Scheduled Tribe", caste), "ST", caste),
          caste = ifelse(grepl("OBC|Other Backward Classes", caste), "OBC", caste))%>%
  mutate(State = case_when(State == "West bengal" ~ "West Bengal",
                            State == "WEST BENGAL" ~ "West Bengal",
                            State == "Up" ~ "UP",
                            TRUE ~ State)) %>%
  mutate(religion = case_when(religion == "Agnostism/ Atheism" ~ "Agnosticism_Atheism",
                              TRUE~ religion))

demovars$gender <- as.factor(demovars$gender)
demovars$caste <- as.factor(demovars$caste)
demovars$urban_rural <- as.factor(demovars$urban_rural)
demovars$age <- as.factor(demovars$age)
demovars$religion <- as.factor(demovars$religion)
demovars$State <- as.factor(demovars$State)

@@

```{r, echo=FALSE}
library(dplyr)

@@

```{r, echo=FALSE}
library(ggplot2)

@@

```{r, echo=FALSE}

@@

wilcox_gender <- demovars %>%
  dplyr::select(starts_with("Risky")) %>%
  lapply(function(col) wilcox.test(col ~ gender, data = demovars))

@@

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)

demovars_caste <- demovars %>%
  dplyr::select(starts_with("Risky"), caste) %>%
  na.omit()

demovars_caste_long <- demovars_caste %>%
  pivot_longer(cols = starts_with("Risky_"), names_to = "technology", values_to = "perceived_risk") %>%
  mutate(technology = gsub("Risky_", "", technology))

@@

# For Coal
Coal_urban_rural <- demovars_urban_rural %>%
  filter(technology == "Coal")
pairwise.wilcox.test(Coal_urban_rural$perceived_risk, Coal_urban_rural$urban_rural, p.adjust.method = "BH")

# For Gas
Gas_urban_rural <- demovars_urban_rural %>%
  filter(technology == "Gas")
pairwise.wilcox.test(Gas_urban_rural$perceived_risk, Gas_urban_rural$urban_rural, p.adjust.method = "BH")

# For Hydro
Hydro_urban_rural <- demovars_urban_rural %>%
  filter(technology == "Hydro")
pairwise.wilcox.test(Hydro_urban_rural$perceived_risk, Hydro_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDBiogas
INDBiogas_urban_rural <- demovars_urban_rural %>%
  filter(technology == "INDBiogas")
pairwise.wilcox.test(INDBiogas_urban_rural$perceived_risk, INDBiogas_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDDiesel
INDDiesel_urban_rural <- demovars_urban_rural %>%
  filter(technology == "INDDiesel")
pairwise.wilcox.test(INDDiesel_urban_rural$perceived_risk, INDDiesel_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDFirewoodetc
INDFirewoodetc_urban_rural <- demovars_urban_rural %>%
  filter(technology == "INDFirewoodetc")
pairwise.wilcox.test(INDFirewoodetc_urban_rural$perceived_risk, INDFirewoodetc_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDHydro
INDHydro_urban_rural <- demovars_urban_rural %>%
  filter(technology == "INDHydro")
pairwise.wilcox.test(INDHydro_urban_rural$perceived_risk, INDHydro_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDKerosene
INDKerosene_urban_rural <- demovars_urban_rural %>%
  filter(technology == "INDKerosene")
pairwise.wilcox.test(INDKerosene_urban_rural$perceived_risk, INDKerosene_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDLPG
INDLPG_urban_rural <- demovars_urban_rural %>%
  filter(technology == "INDLPG")
pairwise.wilcox.test(INDLPG_urban_rural$perceived_risk, INDLPG_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDSolar
INDSolar_urban_rural <- demovars_urban_rural %>%
  filter(technology == "INDSolar")
pairwise.wilcox.test(INDSolar_urban_rural$perceived_risk, INDSolar_urban_rural$urban_rural, p.adjust.method = "BH")

# For INDWind
INDWind_urban_rural <- demovars_urban_rural %>%
 filter(technology == "INDWind")
pairwise.wilcox.test(INDWind_urban_rural$perceived_risk, INDWind_urban_rural$urban_rural, p.adjust.method = "BH")

#For Nuclear
Nuclear_urban_rural <- demovars_urban_rural %>%
filter(technology == "Nuclear")
pairwise.wilcox.test(Nuclear_urban_rural$perceived_risk, Nuclear_urban_rural$urban_rural, p.adjust.method = "BH")

#For Oil
Oil_urban_rural <- demovars_urban_rural %>%
filter(technology == "Oil")
pairwise.wilcox.test(Oil_urban_rural$perceived_risk, Oil_urban_rural$urban_rural, p.adjust.method = "BH")

#For Solar
Solar_urban_rural <- demovars_urban_rural %>%
filter(technology == "Solar")
pairwise.wilcox.test(Solar_urban_rural$perceived_risk, Solar_urban_rural$urban_rural, p.adjust.method = "BH")

#For Wind
Wind_urban_rural <- demovars_urban_rural %>%
filter(technology == "Wind")
pairwise.wilcox.test(Wind_urban_rural$perceived_risk, Wind_urban_rural$urban_rural, p.adjust.method = "BH")

@@

# Convert variables to factors
demovars_urban_rural$urban_rural <- factor(demovars_urban_rural$urban_rural)
demovars_urban_rural$technology <- factor(demovars_urban_rural$technology)

# Create boxplot
ggplot(demovars_urban_rural, aes(x = technology, y = perceived_risk, fill = urban_rural)) +
  stat_boxplot(geom="errorbar", width=0.5) +
  stat_boxplot(geom="boxplot", width=0.5, notch=FALSE, outlier.shape=NA) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800")) +
  labs(x = "Technology", y = "Perceived Risk", fill = "Urban/Rural") +
  theme_bw() +
   theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  ggtitle("Perceived Risk by Technology and Urban/Rural Group") +
  facet_wrap(~ifelse(grepl("^IND", technology), "IND", "Non-IND"), nrow = 1)

```{r}
# now check for urban and gender since caste is not that important , I don't care about age. let's do a regression

str(demovars)

```{r}
library(dplyr)
demovars_subset <- demovars %>%
  na.omit()%>%
  select(-c(urban_rural, gender, caste, religion, age, State))

# correlation matric to check correlations among the DVs
correlation_matrix <- round(cor(demovars_subset), 2)

# Convert correlation matrix to data frame
cor_df <- as.data.frame(as.table(correlation_matrix))

# Rename columns
colnames(cor_df) <- c("Var1", "Var2", "Correlation")

# Extract variables with correlation greater than 0.7
high_corr_vars <- subset(cor_df, abs(Correlation) > 0.7) %>%
                  filter(Var1 != Var2)

# We see that Risky_INDSolar and Risky_Solar are highly correlated concepts (as expected) but rest of the dependent variables are not highly correlated. In the context of dependent variables, high correlation between them can indicate that they are measuring similar constructs or dimensions, which can lead to redundancy in the model. In some cases, it may be necessary to combine these variables or choose one to represent the construct in the analysis. Additionally, high correlation between dependent variables can make it difficult to isolate the effect of individual independent variables on each dependent variable. Therefore, it is important to check the correlation between different dependent variables to ensure that the model is accurately capturing the relationships between the independent and dependent variables.

# Here we don't need to worry about this because we are going to run two separate regression models. one for IND and one for centrally owned technologies. SO NO HIGH MULTICOLINEARITY - GOOD NEWS!

```{r}
# I want to conduct a factor analysis on my IVs to see how closely connected some of the caste and religion categories might be. 
library(psych)

```{r}
# what is the appropriate regression model to use? First I consider the regression model used in risk studies? 
# First question is does WME (upper caste male effect exist in India, or what demographic factors impact risk perception of energy technologies.)
# going to use linear regression - following Kahan et al.

# running multivariate regression model on risk perception fom centrally owned energy technologies:

model_Risky_central <- demovars %>%
  dplyr::select(dplyr::starts_with("Risky"), age, urban_rural, gender, caste, religion, State) %>%
  dplyr::select(-dplyr::starts_with("Risky_IND")) %>%
  na.omit()%>%
#creating dummy variables
  mutate(gender_female = if_else(gender == "Female", 1, 0),
         caste_brahmin = if_else(caste == "Brahmin", 1, 0),
         caste_general = if_else(caste == "General", 1, 0),
         caste_obc = if_else(caste == "OBC", 1, 0),
         caste_rather_not_say = if_else(caste == "Rather not say/Don't know", 1, 0),
         caste_sc = if_else(caste == "SC", 1, 0),
         caste_st = if_else(caste == "ST", 1, 0),
         urban_rural_rural = if_else(urban_rural == "Rural", 1, 0),
         age_18_24 = if_else(age == "18-24 years old", 1, 0),
         age_25_34 = if_else(age == "25-34 years old", 1, 0),
         age_35_44 = if_else(age == "35-44 years old", 1, 0),
         age_45_54 = if_else(age == "45-54 years old", 1, 0),
         age_55_64 = if_else(age == "55-64 years old", 1, 0),
         age_65_74 = if_else(age == "65-74 years old", 1, 0),
         age_75_or_older = if_else(age == "75 years or older", 1, 0),
         religion_agnosticism_atheism = if_else(religion == "Agnosticism_Atheism", 1, 0),
         religion_buddhism = if_else(religion == "Buddhism", 1, 0),
         religion_christanity = if_else(religion == "Christanity", 1, 0),
         religion_hinduism = if_else(religion == "Hinduism", 1, 0),
         religion_islam = if_else(religion == "Islam", 1, 0),
         religion_jainism = if_else(religion == "Jainism", 1, 0),
         religion_other = if_else(religion == "Other", 1, 0),
         religion_sikhism = if_else(religion == "Sikhism", 1, 0),
         state_maharashtra = if_else(State == "Maharashtra", 1, 0),
         state_rajasthan = if_else(State == "Rajasthan", 1, 0),
         state_tamilnadu = if_else(State == "Tamilnadu", 1, 0),
         state_up = if_else(State == "UP", 1, 0),
         state_west_bengal = if_else(State == "West Bengal", 1, 0))

# Fit a multivariate linear regression model
model <- lm(cbind(Risky_Hydro, Risky_Solar, Risky_Wind, Risky_Nuclear, Risky_Coal, Risky_Gas, Risky_Oil) ~ gender_female + caste_general + caste_obc + caste_rather_not_say + caste_sc + caste_st + urban_rural_rural + age_25_34 + age_35_44 + age_45_54 + age_55_64 + age_65_74 + age_75_or_older + religion_buddhism + religion_christanity + religion_hinduism + religion_islam + religion_jainism + religion_other + religion_sikhism + state_rajasthan + state_tamilnadu + state_up + state_west_bengal, data = model_Risky_central)

# Print the model summary
summary(model)

str(model_Risky_central)

#NEXT - plot residuals, read about regression on statistics by Jim. move on to factor analysis and reducing factors and conducting regression models and residual plots, send these to Terre, Milind and Ramana - questions and ideas for two papers. - right now the results from the regression do not match the earlier results like the significance of gender for instance
